Viscous Transport in Eroding Porous Media

### 2019-09-30 docs/transport/erosion_transport.tex
NM

Flow in porous media is further complicated when there is a two-way
coupling between the flow and the geometry. For example, the grains of a
porous media evolve in time in applications involving
melting~\cite{bec-vis1998, rycroft2016asymmetric, favier2019rayleigh,
morrow2019moving}, dissolution~\cite{kan-zha-che-he2002, mac2015shape,
moo2017, wykes2018self}, deposition~\cite{joh-eli1995,
hewett2018modelling}, biofilm growth~\cite{tan-val-wer2015}, and crack
formation~\cite{cho2019crack}. We focus on erosion, a fluid-mechanical
process that is prevalent in many geophysical, hydrological, and
industrial applications~\cite{berhanu2012shape, hewett2017evolution,
lopez2018cfd, allen2019sde, amin2019role}.  When a porous geometry
erodes, certain qualitative characteristics are unveiled that affect
transport through the geometry.  For example, an eroded geometry may
contain channels of high porosity, which, though few in number and
modest in volume fraction, transmit a large portion of the flux. This
arrangement results in velocities that vary over several orders of
magnitude~\cite{all-hea-lab-rei2002}.  Moreover, channelization creates
a heterogeneous and anisotropic medium properties affecting the
transport of tracers such as contaminants~\cite{cve-che-wen1996,
dag1987, kon-bre1978} and heat~\cite{nil-sto1990, ree-sto1995}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Methods}
\label{sec:method}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In line with our previous work~\cite{qua-moo2018}, we use two meshes to
simulate erosion. The integral equation is solved by discretizing the
boundary of the geometry at a set of collocation points distributed
equally in arclength (Section~\ref{sec:spatialDiscretization}).
Depending on the proximity of the target point to the source points, the
quadrature rule is either the trapezoid rule or the Barycentric
quadrature rule (Section~\ref{sec:bary}).  The selection algorithm that
determines which quadrature method is applied is described in
Section~\ref{sec:fmm}.  Once the shear stress is computed, the bodies
are eroded a single time step by using a {\thL}
discretization~\cite{hou-low-she1994}.  The time stepping methods for
erosion and passive particles are described in Section~\ref{sec:time}

>>>>

Flow in porous media is further complicated when there is a two-way
coupling between the flow and the geometry. For example, the grains of a
porous media evolve in time in applications involving
melting~\cite{bec-vis1998, rycroft2016asymmetric, jambon2018singular, favier2019rayleigh, morrow2019moving}, dissolution~\cite{kan-zha-che-he2002, mac2015shape, moo2017, wykes2018self}, deposition~\cite{joh-eli1995,
hewett2018modelling}, biofilm growth~\cite{tan-val-wer2015}, and crack
formation~\cite{cho2019crack}. We focus on erosion, a fluid-mechanical
process that is prevalent in many geophysical, hydrological, and
industrial applications~\cite{berhanu2012shape, hewett2017evolution, lachaussee2018competitive, lopez2018cfd, allen2019sde, amin2019role}.  When a porous geometry erodes, certain qualitative characteristics are unveiled that affect transport through the geometry.  For example, an eroded geometry may
contain channels of high porosity, which, though few in number and
modest in volume fraction, transmit a large portion of the flux. This
arrangement results in velocities that vary over several orders of
magnitude~\cite{all-hea-lab-rei2002}.  Moreover, channelization creates
a heterogeneous and anisotropic medium properties affecting the
transport of tracers such as contaminants~\cite{cve-che-wen1996,
dag1987, kon-bre1978} and heat~\cite{nil-sto1990, ree-sto1995}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Methods}
\label{sec:method}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In line with our previous work~\cite{qua-moo2018}, we use two meshes to
simulate erosion. The integral equation is solved by discretizing the
boundary of the geometry at a set of collocation points distributed
equally in arclength (Section~\ref{sec:spatialDiscretization}).
Depending on the proximity of the target point to the source points, the
quadrature rule is either the trapezoid rule or the Barycentric
quadrature rule (Section~\ref{sec:bary}).  The selection algorithm that
determines which quadrature method is applied is described in
Section~\ref{sec:fmm}.  Once the shear stress is computed, the bodies
are eroded a single time step by using a {\thL}
discretization~\cite{hou-low-she1994, moore2013self}.  The time stepping methods for
erosion and passive particles are described in Section~\ref{sec:time}
